---
title: "hdpsComparisonScript"
author: "Yuxi Tian"
date: "September 18, 2016"
output: pdf_document
---

Install packages
```
install.packages("devtools")
library(devtools)
install_github("ohdsi/OhdsiRTools")
install_github("ohdsi/SqlRender")
install_github("ohdsi/DatabaseConnector")
install_github("ohdsi/Cyclops", ref="HDPS")
install_github("ohdsi/FeatureExtraction")
install_github("ohdsi/CohortMethod", ref = "hdps_clean")
library(CohortMethod)

```

For each exposure/comparator/outcome combination, prepare the cohort tables, as in the Single Studies vignette.

Next prepare the feature sets. Put in relevant inclusion/exclusion conceptIds. As an example, cohortMethodData1 will be the HDPS feature set; cohortMethodData2 will be the FeatureExtraction feature set.
```{r, eval=FALSE}
covarSettings1 = createHdpsCovariateSettings(useCovariateCohortIdIs1 = FALSE,
                                             useCovariateDemographics = TRUE, 
                                             useCovariateDemographicsGender = TRUE,
                                             useCovariateDemographicsRace = TRUE,
                                             useCovariateDemographicsEthnicity = TRUE,
                                             useCovariateDemographicsAge = TRUE, 
                                             useCovariateDemographicsYear = TRUE,
                                             useCovariateDemographicsMonth = TRUE,
                                             useCovariateConditionOccurrence = TRUE,
                                             useCovariate3DigitIcd9Inpatient180d = TRUE,
                                             useCovariate3DigitIcd9Inpatient180dMedF = TRUE,
                                             useCovariate3DigitIcd9Inpatient180d75F = TRUE,
                                             useCovariate3DigitIcd9Ambulatory180d = TRUE,
                                             useCovariate3DigitIcd9Ambulatory180dMedF = TRUE,
                                             useCovariate3DigitIcd9Ambulatory180d75F = TRUE,
                                             useCovariateDrugExposure = TRUE,
                                             useCovariateIngredientExposure180d = TRUE,
                                             useCovariateIngredientExposure180dMedF = TRUE,
                                             useCovariateIngredientExposure180d75F = TRUE,
                                             useCovariateProcedureOccurrence = TRUE,
                                             useCovariateProcedureOccurrenceInpatient180d = TRUE,
                                             useCovariateProcedureOccurrenceInpatient180dMedF = TRUE,
                                             useCovariateProcedureOccurrenceInpatient180d75F = TRUE,
                                             useCovariateProcedureOccurrenceAmbulatory180d = TRUE,
                                             useCovariateProcedureOccurrenceAmbulatory180dMedF = TRUE,
                                             useCovariateProcedureOccurrenceAmbulatory180d75F = TRUE,
                                             excludedCovariateConceptIds = excludedCovariateConceptIds, 
                                             includedCovariateConceptIds = c(),
                                             deleteCovariatesSmallCount = 5)

covariateSettings1 <- createCovariateSettings(useCovariateDemographics = TRUE,
                                              useCovariateDemographicsAge = TRUE,
                                              useCovariateDemographicsGender = TRUE,
                                              useCovariateDemographicsRace = TRUE,
                                              useCovariateDemographicsEthnicity = TRUE,
                                              useCovariateDemographicsYear = TRUE,
                                              useCovariateDemographicsMonth = TRUE,
                                              useCovariateConditionOccurrence = TRUE,
                                              useCovariateConditionOccurrence365d = TRUE,
                                              useCovariateConditionOccurrence30d = TRUE,
                                              useCovariateConditionOccurrenceInpt180d = TRUE,
                                              useCovariateConditionEra = TRUE,
                                              useCovariateConditionEraEver = TRUE,
                                              useCovariateConditionEraOverlap = TRUE,
                                              useCovariateConditionGroup = TRUE,
                                              useCovariateDrugExposure = TRUE,
                                              useCovariateDrugExposure365d = TRUE,
                                              useCovariateDrugExposure30d = TRUE,
                                              useCovariateDrugEra = TRUE,
                                              useCovariateDrugEra365d = TRUE,
                                              useCovariateDrugEra30d = TRUE,
                                              useCovariateDrugEraEver = TRUE,
                                              useCovariateDrugEraOverlap = TRUE,
                                              useCovariateDrugGroup = TRUE,
                                              useCovariateProcedureOccurrence = TRUE,
                                              useCovariateProcedureOccurrence365d = TRUE,
                                              useCovariateProcedureOccurrence30d = TRUE,
                                              useCovariateProcedureGroup = TRUE,
                                              useCovariateObservation = FALSE,
                                              useCovariateObservation365d = FALSE,
                                              useCovariateObservation30d = FALSE,
                                              useCovariateObservationCount365d = FALSE,
                                              useCovariateMeasurement365d = FALSE,
                                              useCovariateMeasurement30d = FALSE,
                                              useCovariateMeasurementCount365d = FALSE,
                                              useCovariateMeasurementBelow = FALSE,
                                              useCovariateMeasurementAbove = FALSE,
                                              useCovariateConceptCounts = FALSE,
                                              useCovariateRiskScores = FALSE,
                                              useCovariateRiskScoresCharlson = FALSE,
                                              useCovariateRiskScoresDCSI = FALSE,
                                              useCovariateRiskScoresCHADS2 = FALSE,
                                              useCovariateInteractionYear = FALSE,
                                              useCovariateInteractionMonth = FALSE,
                                              excludedCovariateConceptIds = excludedCovariateConceptIds,
                                              includedCovariateConceptIds = c(),
                                              deleteCovariatesSmallCount = 5)
```

Run the sql script to get the four relevant cohortMethodData objects:
```{r, eval=FALSE}
cohortMethodData1 = getDbCohortMethodData(blahblah,
                                          covariateSettings = covarSettings1)

cohortMethodData2 = getDbCohortMethodData(blahblah,
                                          covariateSettings = covarSettings2)
```


The following code runs a simulation study. Refer to the documentation for runSimulationStudy for descriptions of parameters. Note the global option fffinalizer is changed so as to not run out of disk space.
```{r,eval=FALSE}
options("fffinalizer" = "delete")

#runSimulationStudy <- function(cohortMethodData, confoundingScheme = 0, confoundingProportion = 0.3, n = 10,
                               # trueBeta = NULL, outcomePrevalence = NULL, crossValidate = TRUE, hdpsFeatures = FALSE,
                               # ignoreCensoring = FALSE, ignoreCensoringCovariates = TRUE) {

# Default runs is n = 10; can be changed
# Currently matching 1-1 on propensity score (strata = matchOnPs(ps))
# To make things run faster just for testing purposes, can set crossValidate = FALSE, won't crossValidate for fitting original data and fitting LASSO propensity score

# Vanilla parameters: no unmeasured confounding, no replacing observed effect size, no replacing observed outcome prevalence
simulationStudy1 <- runSimulationStudy(cohortMethodData1, hdpsFeatures = TRUE)
simulationStudy2 <- runSimulationStudy(cohortMethodData2, hdpsFeatures = FALSE)

# Specify true effect size
simulationStudy1 <- runSimulationStudy(cohortMethodData1, hdpsFeatures = TRUE, trueBeta = 1.0)
simulationStudy2 <- runSimulationStudy(cohortMethodData2, hdpsFeatures = FALSE, trueBeta = 1.0)

# Specify outcome prevalence
simulationStudy1 <- runSimulationStudy(cohortMethodData1, hdpsFeatures = TRUE, outcomePrevalence = .05)
simulationStudy2 <- runSimulationStudy(cohortMethodData2, hdpsFeatures = FALSE, outcomePrevalence = .05)

# Remove demographics to simulate unmeasured confounding in propensity score
simulationStudy1 <- runSimulationStudy(cohortMethodData1, hdpsFeatures = TRUE, confoundingScheme = 1)
simulationStudy2 <- runSimulationStudy(cohortMethodData2, hdpsFeatures = FALSE, confoundingScheme = 1)

# Remove random covariates to simulate unmeasured confounding in propensity score; here removes 25%
simulationStudy1 <- runSimulationStudy(cohortMethodData1, hdpsFeatures = TRUE, confoundingScheme = 2, confoundingProportion = 0.25)
simulationStudy2 <- runSimulationStudy(cohortMethodData2, hdpsFeatures = FALSE, confoundingScheme = 2, confoundingProportion = 0.25)

options("fffinalizer" = NULL)

```

The following code demonstrates some of the return values of runSimulationStudy
```{r,eval=FALSE}

# View coefficients used in true outcome model
trueOutcomeModel = simulationStudy1$trueOutcomeModel

# View true effect size used in simulation
trueEffectSize = simulationStudy1$trueEffectSize

# View estimates generated via different propensity scores
logRRLasso = simulationStudy1$estimatesLasso$logRr
logRRExposure = simulationStudy1$estimatesExpHdps$logRr
logRRBias = simulationStudy1$estimatesBiasHdps$logRr
mean(logRRLasso)
sd(logRRLasso)
mean(logRRExposure)
sd(logRRExposure)
mean(logRRBias)
sd(logRRBias)

# View auc
aucLasso = simulationStudy1$aucLasso
aucExpHdps = simulationStudy1$aucExpHdps
aucBiasHdps = simulationStudy1$aucBiasHdps

# View propensity scores for each method
psLasso = simulationStudy1$psLasso
psExp = simulationStudy1$psExp
psBias = simulationStudy1$psBias

# Do things with the propensity scores to assess balance
strataLasso = matchOnPs(psLasso)
balance = computeCovariateBalance(strataLasso, cohortMethodData1)

```
