---
title: "Populating the study package"
author: "Jenna M. Reps"
date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
vignette: >
  %\VignetteIndexEntry{Populating the study package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
  ```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(PatientLevelPrediction)
knitr::opts_chunk$set(
  cache=FALSE,
  comment = "#>",
  error = FALSE,
  tidy = FALSE)
```
# Introduction

This vignette describes how one can populate the SkeletonExistingModelStudy pacakge with the target cohort, outcome cohorts and model settings.


First make sure to open the Skeleton R project in R studio, this can be done by finding the SkeletonExistingModelStudy.Rproj file in the folder.  Once the package project is opened in R studio there are 3 steps that must be followed:
  
1. Run the function: populatePackage (found in extras/populatePackage.R on line 51) to add all cohorts and settings into the study package
2. Build the study package
3. Run the study package execute function

## Step 1: Populate skeleton settings
All the settings can be added to the study package by using the function 'populatePackage()' that is found in extras/populatePackage.R.

To add the function to your environment, make sure the package R project is open in R studio and run:
  ```{r, eval=FALSE}
source('./extras/populatePackage.R')
```

This will make the function 'populatePackage()'available to use within your R session.  

The 'populatePackage()' function requires users to specify:

* targetCohortId - The ATLAS id for the target cohort 
* targetCohortName - A string with a sharable name for the target cohort
* outcomeId - The ATLAS id for the outcome cohort 
* outcomeName - A string with a sharable name for the outcome cohort
* standardCovariates - A data.frame with the columns: covariateId (for standard fetures using FeatureExtraction), covariateName and points to assign points for standard covariates 
* baseUrl - The url for the ATLAS webapi (this will be used to extract the ATLAS cohorts)
* atlasIds - an integer or vector of integers specifying the atlas cohort Ids that are used by the custom cohort covariates
* atlasNames - a string or vector of strings specifying the names of the atlas ids (must be the same length as atlasIds)
* startDays - a negative integer or vector of negative integers specifying the days relative to index to start looking for the patient  being in the covariate cohort 
* endDays - a negative integer (or zero) or vector of negative integers (or zero) specifying the days relative to index to stop looking for the patient being in the covariate cohort 
* points - a double or vector of doubles specifying the points corresponding to each variable

For example, to create two custom cohort covariates into the package I can run:
```{r, eval=FALSE}
populatePackage(targetCohortId = 10845,
                targetCohortName = 'neg mamo',
                outcomeId = 10082,
                outcomeName = 'breast cancer',
                standardCovariates = data.frame(covariateId = c(0003, 1003,
                                                                2003, 3003,
                                                                4003, 5003,
                                                                6003, 7003,
                                                                8003, 9003,
                                                                10003, 11003,
                                                                12003, 13003,
                                                                14003, 15003,
                                                                16003, 17003,
                                                                8507001),
                                                covariateName = c('Age 0-4', 'Age 5-9',
                                                                  'Age 10-14', 'Age 15-19',
                                                                  'Age 20-24', 'Age 25-30',
                                                                  'Age 30-34', 'Age 35-40',
                                                                  'Age 40-44', 'Age 45-50',
                                                                  'Age 50-54', 'Age 55-60',
                                                                  'Age 60-64', 'Age 65-70',
                                                                  'Age 70-74', 'Age 75-80',
                                                                  'Age 80-84', 'Age 85-90',
                                                                  'Male'), 
                                                points = c(rep(0,19))),
                baseUrl = 'https://yourWebAPI',
                atlasCovariateIds = c(14709,14709, 14710),
                atlasCovariateNames = c('smoking anytime', 'smoking recent', 'traumatic brain injury'),
                startDays = c(-999,-30,-999),
                endDays =  c(0,0,0),
                points = c(1,2,1))
```

The code above extracts the target and outcome cohorts and two ATLAS cohort (14709, 14710) to create three covariates:

* covariate 1: The ATLAS cohort with the id of 14709 named 'smoking anytime'  looks for patients who have a smoking anytime cohort_start_date between (index date-999 days) and (index date).  E.g., If a patient is in the smoking anytime cohort 50 days before the index date then they will have a value of 1 for the custom covariate.  If they are not in the smoking anytime cohort between 999 days before index and the day of index then they will have a value of 0 for the custom covariate.
* covariate 2: The ATLAS cohort with the id of 14709 named 'smoking recent' looks for patients who have a smoking recent cohort_start_date between (index date-30 days) and (index date).  E.g., If a patient is in the smoking recent cohort 20 days before the index date then they will have a value of 1 for the custom covariate.  If they are not in the smoking recent cohort between 30 days before index and the day of index then they will have a value of 0 for the custom covariate.
* covariate 3: The ATLAS cohort with the id of 14710 named 'traumatic brain injury' looks for patients who have a traumatic brain injury cohort_start_date between (index date-999 days) and (index date).  E.g., If a patient is in the traumatic brain injury cohort 200 days before the index date then they will have a value of 1 for the custom covariate.  If they are not in the traumatic brain injury cohort before index  then they will have a value of 0 for the custom covariate.

It also creates three csv files in the inst/settings directory named: 

* CohortsToCreate.csv - specifying the target and outcome cohorts
* CustomCovariates.csv - specifying the custom covariates
* SimpleModel.csv - settings specifying the simple prediction model

## Step 2: Build the study package
Aftering adding the settings into the package, you now need to build the package. Use the standard process (in R studio press the 'Build' tab in the top right corner and then select the 'Install and Restart' button) to build the study package so an R library is created.

## Step 3: Execute the study to validate an existing model

```{r eval=FALSE}
  library(SkeletonExistingModelStudy)
  options(fftempdir = "location with space to save big data")
  
  # The folder where the study intermediate and result files will be written:
  outputFolder <- "./SkeletonExistingModelStudyResults"
  
  # Details for connecting to the server:
  dbms <- "you dbms"
  user <- 'your username'
  pw <- 'your password'
  server <- 'your server'
  port <- 'your port'
  
  connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = dbms,
                                                                  server = server,
                                                                  user = user,
                                                                  password = pw,
                                                                  port = port)
  
  # Add the database containing the OMOP CDM data
  cdmDatabaseSchema <- 'cdm database schema'
  # Add a database with read/write access as this is where the cohorts will be generated
  cohortDatabaseSchema <- 'work database schema'
  
  oracleTempSchema <- NULL
  
  # table name where the cohorts will be generated
  cohortTable <- 'SkeletonPredictionStudyCohort'
  
  # TAR settings
  sampleSize <- NULL
  riskWindowStart <- 1
  startAnchor <- 'cohort start'
  riskWindowEnd <- 365
  endAnchor <- 'cohort start'
  firstExposureOnly <- F
  removeSubjectsWithPriorOutcome <- F
  priorOutcomeLookback <- 99999
  requireTimeAtRisk <- F
  minTimeAtRisk <- 1
  includeAllOutcomes <- T
  
  
  #=======================
  
  standardCovariates <- FeatureExtraction::createCovariateSettings(useDemographicsAgeGroup = T, useDemographicsGender = T)
  
  SkeletonExistingModelStudy::execute(connectionDetails = connectionDetails,
                                      cdmDatabaseSchema = cdmDatabaseSchema,
                                      cdmDatabaseName = cdmDatabaseName,
                                      cohortDatabaseSchema = cohortDatabaseSchema,
                                      cohortTable = cohortTable,
                                      sampleSize = sampleSize,
                                      riskWindowStart = riskWindowStart,
                                      startAnchor = startAnchor,
                                      riskWindowEnd = riskWindowEnd,
                                      endAnchor = endAnchor,
                                      firstExposureOnly = firstExposureOnly,
                                      removeSubjectsWithPriorOutcome = removeSubjectsWithPriorOutcome,
                                      priorOutcomeLookback = priorOutcomeLookback,
                                      requireTimeAtRisk = requireTimeAtRisk,
                                      minTimeAtRisk = minTimeAtRisk,
                                      includeAllOutcomes = includeAllOutcomes,
                                      standardCovariates = standardCovariates,
                                      outputFolder = outputFolder,
                                      createCohorts = T,
                                      runAnalyses = T,
                                      viewShiny = T,
                                      packageResults = F,
                                      minCellCount= 5,
                                      verbosity = "INFO",
                                      cdmVersion = 5)
)
```
