---
title: "Using the package skeleton for validating existing model studies"
author: "Jenna M. Reps"
date: "`r Sys.Date()`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
vignette: >
  %\VignetteIndexEntry{Using the package skeleton for validating existing model studies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
  ```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(PatientLevelPrediction)
knitr::opts_chunk$set(
  cache=FALSE,
  comment = "#>",
  error = FALSE,
  tidy = FALSE)
```
# Introduction

This vignette describes how one can use the package skeleton for validating existing prediction model studies to create one's own study package. This skeleton is aimed at patient-level prediction studies using the `PatientLevelPrediction` package. The resulting package can be used to execute the study at any site that has access to an observational database in the Common Data Model. It will perform the following steps:

1. Instantiate all cohorts needed for the study in a study-specific cohort table. 
2. The main analysis will be executed using the `PatientLevelPrediction` package, which involves applying and validating existing prediction models.
3. The results can be modified to remove sensitive data ready for sharing.

The package skeleton currently implements an examplar study, validating CHADS2. If desired (as a test), one can run the package as is. 

## Open the project in Rstudio
Make sure to have RStudio installed.  Then open the R project downloaded from ATLAS by decompressing the downloaded folder and clicking on the <SkeletonExistingModelStudy>.Rproj file (where <SkeletonExistingModelStudy> is replaced by the study name you specified in ATLAS).  This should open an RStudio session.


## Installing all package dependencies 
Before you can build the package you downloaded from ATLAS you need to make sure you have all the dependencies:

```{r eval=FALSE}
source('./extras/packageDeps.R')
```

## Building the package
Once you have the dependencies installed you can now build the R package.  This creates a library you can load to run the validation study.  To build the package click 'Build' on the top right hand side tab menu (there are tabs: 'Environment', 'History', 'Connections', 'Build', 'Git').  Once in 'Build' click the 'Install and Restart' button.  This will now build your package and create the R library.  If it succeeds you will see '* DONE (<SkeletonExistingModelStudy>)', if it fails you will see red output and the library may not be created.  Please report an issue to: https://github.com/OHDSI/PatientLevelPrediction/issues if your library does not get created.

## Running the package

To run the study, open the extras/CodeToRun.R R script (the file called `CodeToRun.R` in the `extras` folder).  This folder specifies the R variables you need to define (e.g., outputFolder and database connection settings). See the R help system for details:

```{r eval=FALSE}
library(SkeletonExistingModelStudy)
?execute
```

By default all the options are set to F for the execute fuction:
```{r eval=FALSE}
options(fftempdir = "location with space to save big data")

# The folder where the study intermediate and result files will be written:
outputFolder <- "./SkeletonExistingModelStudyResults"

# Details for connecting to the server:
dbms <- "you dbms"
user <- 'your username'
pw <- 'your password'
server <- 'your server'
port <- 'your port'

connectionDetails <- DatabaseConnector::createConnectionDetails(dbms = dbms,
                                                                server = server,
                                                                user = user,
                                                                password = pw,
                                                                port = port)

# Add the database containing the OMOP CDM data
cdmDatabaseSchema <- 'cdm database schema'
# Add a database with read/write access as this is where the cohorts will be generated
cohortDatabaseSchema <- 'work database schema'

oracleTempSchema <- NULL

# table name where the cohorts will be generated
cohortTable <- 'SkeletonPredictionStudyCohort'

# TAR settings
sampleSize <- NULL
riskWindowStart <- 1
startAnchor <- 'cohort start'
riskWindowEnd <- 365
endAnchor <- 'cohort start'
firstExposureOnly <- F
removeSubjectsWithPriorOutcome <- F
priorOutcomeLookback <- 99999
requireTimeAtRisk <- F
minTimeAtRisk <- 1
includeAllOutcomes <- T


#=======================

standardCovariates <- FeatureExtraction::createCovariateSettings(useDemographicsAgeGroup = T, useDemographicsGender = T)

SkeletonExistingModelStudy::execute(connectionDetails = connectionDetails,
                                    cdmDatabaseSchema = cdmDatabaseSchema,
                                    cdmDatabaseName = cdmDatabaseName,
                                    cohortDatabaseSchema = cohortDatabaseSchema,
                                    cohortTable = cohortTable,
                                    sampleSize = sampleSize,
                                    riskWindowStart = riskWindowStart,
                                    startAnchor = startAnchor,
                                    riskWindowEnd = riskWindowEnd,
                                    endAnchor = endAnchor,
                                    firstExposureOnly = firstExposureOnly,
                                    removeSubjectsWithPriorOutcome = removeSubjectsWithPriorOutcome,
                                    priorOutcomeLookback = priorOutcomeLookback,
                                    requireTimeAtRisk = requireTimeAtRisk,
                                    minTimeAtRisk = minTimeAtRisk,
                                    includeAllOutcomes = includeAllOutcomes,
                                    standardCovariates = standardCovariates,
                                    outputFolder = outputFolder,
                                    createCohorts = T,
                                    runAnalyses = T,
                                    viewShiny = T,
                                    packageResults = F,
                                    minCellCount= 5,
                                    verbosity = "INFO",
                                    cdmVersion = 5)

```

If you run the above nothing will happen as each option is false.  See the table below for information about each of the inputs.

```{r tableInputs, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "   
| Input | Description | Example |
| --------------| -------------------------------| ---------------- |
| connectionDetails | The details to connected to your OMOP CDM database - use DatabaseConnector package's createConnectionDetails() | createConnectionDetails( dbms = 'postgresql', server = 'database server', user = 'my username', password = 'donotshare', port = 'database port') |
  | cdmDatabaseSchema | The schema containing your OMOP CDM data | 'my_cdm_data.dbo' |
  | cdmDatabaseName | A shareable name for the OMOP CDM data | 'My data' |
  | oracleTempSchema | The temp schema if dbms = 'oracle' - NULL for other dbms | 'my_temp.dbo'|
  | cohortDatabaseSchema | The schema where you have an existing cohort table or where the package will create a cohort table and insert the study cohorts | 'scratch.dbo' |
  | cohortTable | The table name where you cohorts will be written (if creating the cohort pick an unused table name) | 'myTable'|
  | sampleSize | Sample from the target population] | NULL |
  | riskWindowStart | The time at risk starts this many days after the endAnchor | 1 |
  | startAnchor | Make the time-at-risk start relative to cohort start or cohort end | 'cohort start' |          | riskWindowEnd | The time at risk ends this many days after the endAnchor | 365 |
  | endAnchor | Make the time-at-risk end relative to cohort start or cohort end | 'cohort start' |
  | firstExposureOnly | If a patient in the target population at different times restrict to first time? | T | 
  | removeSubjectsWithPriorOutcome | Remove people with the outcome before index? | T | 
  | priorOutcomeLookback | Time to look back from index if removeSubjectsWithPriorOutcome = T  | 9999 |          | requireTimeAtRisk  | Require that a patient must satisfy a minimum time at risk to be in the target population  | F |
  | minTimeAtRisk  | Minimum time at risk a patient must satisfy to be in the target population (used when requireTimeAtRisk = T) | 1 |
  | includeAllOutcomes | Whether to keep people with the outcome during TAR even if they dont have complete follow-up| F |
  | standardCovariates | Standard covariate settings| FeatureExtraction:: createCovariateSettings() |
  | outputFolder | The location where the results of the study will be saved | 'C:/amazingResults'|
  | createCohorts | TRUE or FALSE indicating whether to create the target population and outcome cohorts for the study | TRUE |
  | runAnalyses | TRUE or FALSE indicating whether to run the study analysis - developing and internally validating the models | TRUE |
  | packageResults | TRUE or FALSE indicating whether to remove sensitive counts (determined by the minCellCount input) or sensitive information from the results and creates a zipped file with results that are safe to share (saved to the outputFolder location).  Note: This requires running the study successfully first.  | TRUE |
  | minCellCount | integer that determines the minimum result count required when sharing the results. Any result table cells with counts < minCellCount are replaced with -1 to prevent identification issues with rare diseases | 10 |
  | viewShiny | TRUE or FALSE indicating whether to view a shiny app with the results from the study, Note: This requires running the study successfully first.  | TRUE |
 
  "
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


To create the target and outcome cohorts (cohorts are created into cohortDatabaseSchema.cohortTable)
```{r eval=FALSE}
    createCohorts = T
```

To  validate the models in the study run the code:
```{r eval=FALSE}
    runAnalyses = T
```

If the study runs and you get results, you can then interactively explore the results by running:
```{r eval=FALSE}
    viewShiny= T
```

To package the results ready for sharing with others you can set:    
```{r eval=FALSE}
    packageResults = T
```


## Results
After running the study you will find the result in the `[outputFolder]`/`cdmDatabaseName` directory as an rds object named 'validationResult.rds'.

The validationResult object is a list containing:

```{r tablePlpResult, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "  
| Object | Description | Edited by packageResult |
  | ----------------- | --------------------------------------| -------------|
  | `inputSetting` | All the settings required to reproduce the study | Yes - passwords and database settings are removed | 
  | `executionSummary` | Information about the R version, PatientLevelPrediction version and execution platform info | No | 
  | `model` | The trained model | No | 
  | `analysisRef` | Used to store a unique reference for the study | No | 
  | `covariateSummary` | A dataframe with summary information about how often the covariates occured for those with and without the outcome | Yes - minCellCounts censored | 
  | `performanceEvaluation$ evaluationStatistics` | Performance metrics and sizes | No | 
  | `performanceEvaluation$ thresholdSummary` | Operating characteristcs @ 100 thresholds | Yes | 
  | `performanceEvaluation$ demographicSummary` | Calibration per age group | Yes | 
  | `performanceEvaluation$ calibrationSummary` | Calibration at risk score deciles | Yes | 
  | `performanceEvaluation$ predictionDistribution` | Distribution of risk score for those with and without the outcome | Yes | 
  "
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```


## extras/PackageMaintenance.R
This file contains other useful code to be used only by the package developer (you), such as code to generate the package manual, and code to insert cohort definitions into the package. All statements in this file assume the current working directory is set to the root of the package.



